%!TEX program = xelatex
\documentclass[12pt,a4paper,sans]{moderncv}

\usepackage{amsmath,amssymb,amsthm} 
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{footmisc}

\moderncvstyle{classic} %classic/banking/casual
\moderncvcolor{green}
\moderncvicons{awesome}

% Font setup
\setsansfont{Metric-Light}[Ligatures=TeX,ItalicFont=Metric-LightItalic,BoldFont=Metric-Medium,BoldItalicFont=Metric-MediumItalic]
\setmonofont[BoldFont=GTPressuraMono-Bold,ItalicFont=GTPressuraMono-LightItalic]{GTPressuraMono-Light}

% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\name{Dr.ir.\ Ken}{Arroyo Ohori}
% \title{Curriculum vit\ae{}}         
\address{3D geoinformation, TU Delft}{Julianalaan 134}{2628 BL Delft, the Netherlands}
\email{k.ohori@tudelft.nl}
\homepage{3d.bk.tudelft.nl/ken}

\begin{document}

\recipient{Dr. Magnus Heitzler}{ETH Zurich}
\date{November 13, 2020}
\opening{To the selection committee,}
\closing{Best regards,}
% \enclosure[Following]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle
I am writing to you to support Felix Dahle for your open position as \emph{Doctoral candidate in geoinformatics / cartography} at ETH Zurich.
I had the pleasure to first teach Felix and then to supervise his MSc thesis at TU Delft.

Felix was an excellent student in our MSc in Geomatics programme, graduating cum laude based on his very good course marks and outstanding thesis work.
He knows how to work independently, is organised and already has very good research and writing skills.

After reading your open position description, I am rather impressed by how much Felix is suited for it.
He has expertise in all of the fields you have listed, did an excellent thesis with me on image analysis with feature extraction and machine learning, worked with vectorisation libraries in the course I taught him, has strong Python programming skills, and I am certain that he is well acquainted with geospatial formats because of his coursework in the Geomatics programme.

From the start of his graduation project, Felix told me that he was very interested in pursuing a PhD.
I strongly believe that he is very well suited for this and would have preferred it if he were able to stay in our research group.
Alas, despite my best efforts, I was not able to find an appropriate position for him in our group.

Feel free to contact me if you have any questions.
I would be happy to vouch for Felix, both personally and for the quality of his work.

\makeletterclosing

\end{document}
